\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-06-29 eg6-letters/NIM/EG6_RTPC_NIM.tex
Typo in the NIM abstract
Couple of typos

\begin{abstract}
A new Radial Time Projection Chamber (RTPC) was developed at the Jefferson 
Laboratory to track low-energy nuclear recoils for the purpose of measuring
exclusive nuclear reactions, such as coherent Deeply Virtual Compton Scattering
and coherent meson production off $^4$He. In such processes, the $^4$He nucleus
remains intact in the final state, however the CEBAF Large
Acceptance Spectrometer (CLAS) cannot track the low energy $\alpha$ particles. In
2009, we carried out measurements using the CLAS spectrometer supplemented by
the RTPC positioned directly around a gaseous $^4$He target, allowing a detection
threshold as low as 12~MeV for $^4$He. This article discuses the design,
principle of operation, calibration methods and the performances of this RTPC.
\end{abstract}

@@

The readout system is based on the Front End Electronic (FEE) boards originally 
developed for the ALICE TPC readout system at CERN~\cite{ALICE-FEE}. Each 
readout channel is made of three main components: a charge sensitive, low 
impedance shaping amplifier, a 10 bit, 25-MHz digitizer, and a digital circuit 
that implements online-processing algorithms (pedestal subtraction, zero 
suppression, and tail cancellation). The amplifier is implemented in a 
fully-analogue ASIC, PASA~\cite{ALICE-PASA}, while the signal 
digitization and elaboration part is implemented in the digital ASIC, 
ALTRO~\cite{ALICE-ALTRO}. Both ASICs host 16 channels. The full readout 
chain is implemented on a single Front End Card (FEC), hosting 128 channels. 
FECs are hosted in custom crates, mounted close to the detector. A readout 
control unit (RCU) board is used to distribute the trigger signal to FECs 
and for data readout. Each RCU can handle up to 25 FECs with communication 
between them performed trough a 
custom back-plane, implementing a low-Voltage signal bus. The RCU communicates 
with the CLAS data acquisition (DAQ) system 
trough a 200 MB/s optical link, connected to a data acquisition PC hosting 
a ReadOut Receiver Card (RORC) used to interface with 
the CLAS DAQ system. An Ethernet link is also present, for slow-controls and 
monitoring.

@@

Due to the non perfect experimental conditions, in particular variations in the 
gas mixture~\footnote{It was noted during the experiment that leaks appeared
and the gas flow had to be increased in few occasions to compensate for this.}, 
the drift speed changes during the three months long experimental run.  
Figure~\ref{fig:Drift_run_number_1} shows the $T_{Max/2}$ values for 
individual runs (approximately 2 hours long). We observe a significant 
variation of the drift speed over time that need to be accounted for 
in track reconstruction.

>>>>

\begin{abstract}
A new Radial Time Projection Chamber (RTPC) was developed at the Jefferson 
Laboratory to track low-energy nuclear recoils for the purpose of measuring
exclusive nuclear reactions, such as coherent Deeply Virtual Compton Scattering
and coherent meson production off $^4$He. In such processes, the $^4$He nucleus
remains intact in the final state, however the CEBAF Large
Acceptance Spectrometer (CLAS) cannot track the low energy $\alpha$ particles. In
2009, we carried out measurements using the CLAS spectrometer supplemented by
the RTPC positioned directly around a gaseous $^4$He target, allowing a detection
threshold as low as 12~MeV for $^4$He. This article discusses the design,
principle of operation, calibration methods and the performances of this RTPC.
\end{abstract}

@@

The readout system is based on the Front End Electronic (FEE) boards originally 
developed for the ALICE TPC readout system at CERN~\cite{ALICE-FEE}. Each 
readout channel is made of three main components: a charge sensitive, low 
impedance shaping amplifier, a 10 bit, 25-MHz digitizer, and a digital circuit 
that implements online-processing algorithms (pedestal subtraction, zero 
suppression, and tail cancellation). The amplifier is implemented in a 
fully-analogue ASIC, PASA~\cite{ALICE-PASA}, while the signal 
digitization and elaboration part is implemented in the digital ASIC, 
ALTRO~\cite{ALICE-ALTRO}. Both ASICs host 16 channels. The full readout 
chain is implemented on a single Front End Card (FEC), hosting 128 channels. 
FECs are hosted in custom crates, mounted close to the detector. A readout 
control unit (RCU) board is used to distribute the trigger signal to FECs 
and for data readout. Each RCU can handle up to 25 FECs with communication 
between them performed through a 
custom back-plane, implementing a low-Voltage signal bus. The RCU communicates 
with the CLAS data acquisition (DAQ) system 
trough a 200 MB/s optical link, connected to a data acquisition PC hosting 
a ReadOut Receiver Card (RORC) used to interface with 
the CLAS DAQ system. An Ethernet link is also present, for slow-controls and 
monitoring.

@@

Due to the non perfect experimental conditions, in particular variations in the 
gas mixture\footnote{It was noted during the experiment that leaks appeared,
most likely in one of the $4 \mu$m foils between the beam and drift regions,
and the gas flow had to be increased in few occasions to compensate for this.}, 
the drift speed changes during the three months long experimental run.  
Figure~\ref{fig:Drift_run_number_1} shows the $T_{Max/2}$ values for 
individual runs (approximately 2 hours long). We observe a significant 
variation of the drift speed over time that need to be accounted for 
in track reconstruction.
